Consumer extinctions constrain phenotypic evolution in the resulting food web

### 2019-09-18 analyses/reproduce_analyses.Rmd
update analyses with evolvability

# Arrow data
gradients_Diam.Clutch <- data.frame(Foodweb = c("Original","Extinction"),
                                    sc.Diam = c(0,0), 
                                    sc.log.Clutch = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean))

gradients_Clutch.Pref <- data.frame(Foodweb = c("Original","Extinction"),
                                    sc.sqrt.Pref = c(0,0), 
                                    sc.log.Clutch = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean))

gradients_Diam.Pref <- data.frame(Foodweb = c("Original","Extinction"),
                                    sc.Diam = c(0,0), 
                                    sc.sqrt.Pref = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean))

@@

eggptoid_selection_plot <- eggptoid_plot_df %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
  geom_line(color=cbPalette[5]) +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall midge preference (SDs)") + 
  ylab(expression(paste(Delta," egg parasitoid survival (original - extinction)"))) +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  geom_hline(yintercept=0, linetype="dotted") +
  theme_cowplot(font_size = 12)

>>>>

# Arrow data
gradients_Diam.Clutch <- data.frame(Foodweb = c("Original","Removal"),
                                    sc.Diam = c(0,0), 
                                    sc.log.Clutch = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean))

gradients_Clutch.Pref <- data.frame(Foodweb = c("Original","Removal"),
                                    sc.sqrt.Pref = c(0,0), 
                                    sc.log.Clutch = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean))

gradients_Diam.Pref <- data.frame(Foodweb = c("Original","Removal"),
                                    sc.Diam = c(0,0), 
                                    sc.sqrt.Pref = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean, 
                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean))

@@

eggptoid_selection_plot <- eggptoid_plot_df %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
  geom_line(color=cbPalette[5]) +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall midge preference (SDs)") + 
  ylab(expression(paste(Delta," egg parasitoid survival (original - removal)"))) +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  geom_hline(yintercept=0, linetype="dotted") +
  theme_cowplot(font_size = 12)
